A geo-referenced micro-data set of real estate listings for Spain’s three largest cities

### 2022-02-18 EPB/EPB.Rmd
Declaración de intereses

The authors wish to thank Alessandro Galesi for his support in the paper revision and  Juan  Ramón  Selva  for  collecting  and  cleaning  the  spatial  data.  This  work  has been partially funded by the Spanish Ministry of Economy and Competitiveness Grant PID2019-107800GB-100.

>>>>

Author One and author Two are employed by Idealista. They have been granted permission to share the data presented in this article. None of the authors have financial interests or personal relationships which have, or could be perceived to have, influenced the work reported in this article.
